---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `MRCV`: Methods for Analyzing Multiple Response Categorical Variables (MRCVs)


###### Version : [`r getNamespaceVersion("MRCV")`](https://myaseen208.com/MRCV/); Copyright (C) 2013-2024: License: [GPL-3](https://www.r-project.org/Licenses/)


##### *Natalie Koziol^1^, and Chris Bilder^2^*
1. [Nebraska Center for Research on Children, Youth, Families and Schools (CYFS), University of Nebraska Lincoln, NE, USA](https://cyfs.unl.edu/personnel/bios/koziol-natalie.php)
2. [Department of Statistics, University of Nebraska-Lincoln, Lincoln NE, USA](https://www.chrisbilder.com/)

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/MRCV)](https://cran.r-project.org/package=MRCV)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/MRCV?color=green)](https://CRAN.R-project.org/package=MRCV)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/MRCV) -->

```{r, results='asis', echo=FALSE}
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("MRCV")) != "",
               yes = getNamespaceVersion("MRCV"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/MRCV", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/MRCV", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/MRCV)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/MRCV/total.svg)] -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/MRCV)
***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("MRCV", fields = "Description")))`

## Installation
The package can be installed from CRAN as follows:

```{r, eval=FALSE}
install.packages("MRCV", dependencies = TRUE)
```


## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package = "MRCV")
```

## Links

[CRAN page](https://cran.r-project.org/package=MRCV)



## Citing `MRCV`
To cite the package use:


```{r, comment = ""}
citation("MRCV")
```
